Choosing Color Palettes for Statistical Graphics

### 2006-09-07 trunk/vcd/paper/Color/draft.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@560 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=\textwidth}
\begin{figure}[b!]
\begin{center}
<<pal-s-construct>>=
if(generate_png) {
  png(file = "pal-s-construct.png", height = 420, width = 840)
  par(mfrow = c(1, 2))
  hue.slice(260, grid.n = 301, main = "H = 260")
  lines(c(0, 100), c(90, 50), lty = 2)
  lines(c(0, 80), c(90, 30), lty = 2)
  lines(c(2.5, 2.5), c(90, 30), lty = 2)
  rect(0, 87.5, 5, 92.5, col = hcl(260, 0, 90))
  rect(47.5, 67.5, 52.5, 72.5, col = hcl(260, 50, 70))
  rect(95, 47.5, 100, 52.5, col = hcl(260, 100, 50))
  rect(37.5, 57.5, 42.5, 62.5, col = hcl(260, 40, 60))
  rect(77.5, 27.5, 82.5, 32.5, col = hcl(260, 80, 30))
  rect(0, 57.5, 5, 62.5, col = hcl(260, 0, 60))
  rect(0, 27.5, 5, 32.5, col = hcl(260, 0, 30))
  hue.slice(120, grid.n = 301, main = "H = 120")
  lines(c(0, 100), c(90, 75), lty = 2)
  lines(c(2.5, 2.5), c(90, 30), lty = 2)
  rect(0, 87.5, 5, 92.5, col = hcl(260, 0, 90))
  rect(47.5, 80, 52.5, 85, col = hcl(120, 50, 82.5))
  rect(95, 72.5, 100, 77.5, col = hcl(120, 100, 75))
  rect(0, 57.5, 5, 62.5, col = hcl(260, 0, 60))
  rect(0, 27.5, 5, 32.5, col = hcl(260, 0, 30))
  dev.off()
}
@
\includegraphics{pal-s-construct}
\caption{\label{fig:pal-s-construct} Constructing sequential palettes. The chroma/luminance
plane is show for two hues $H = 260$ (left) and $H = 120$ (right). Colors are chosen by varying
either only luminance or both luminance and chroma.}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=\textwidth}
\begin{figure}[b!]
\begin{center}
<<pal-s-construct>>=
if(generate_png) {
  png(file = "pal-s-construct.png", height = 420, width = 840)
  par(mfrow = c(1, 2))
  hue.slice(260, grid.n = 301)
  lines(c(0, 100), c(90, 50), lty = 2)
  lines(c(0, 80), c(90, 30), lty = 2)
  lines(c(2.5, 2.5), c(90, 30), lty = 2)
  rect(0, 87.5, 5, 92.5, col = hcl(260, 0, 90))
  rect(47.5, 67.5, 52.5, 72.5, col = hcl(260, 50, 70))
  rect(95, 47.5, 100, 52.5, col = hcl(260, 100, 50))
  rect(37.5, 57.5, 42.5, 62.5, col = hcl(260, 40, 60))
  rect(77.5, 27.5, 82.5, 32.5, col = hcl(260, 80, 30))
  rect(0, 57.5, 5, 62.5, col = hcl(260, 0, 60))
  rect(0, 27.5, 5, 32.5, col = hcl(260, 0, 30))
  hue.slice(120, grid.n = 301)
  lines(c(0, 100), c(90, 75), lty = 2)
  lines(c(2.5, 2.5), c(90, 30), lty = 2)
  rect(0, 87.5, 5, 92.5, col = hcl(260, 0, 90))
  rect(47.5, 80, 52.5, 85, col = hcl(120, 50, 82.5))
  rect(95, 72.5, 100, 77.5, col = hcl(120, 100, 75))
  rect(0, 57.5, 5, 62.5, col = hcl(260, 0, 60))
  rect(0, 27.5, 5, 32.5, col = hcl(260, 0, 30))
  dev.off()
}
@
\includegraphics{pal-s-construct}
\caption{\label{fig:pal-s-construct} Constructing sequential palettes. The chroma/luminance
plane is show for two hues $H = 260$ (left) and $H = 120$ (right). Colors are chosen by varying
either only luminance or both luminance and chroma.}
\end{center}
\end{figure}
